Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-26 src/tex/methods.tex
move plot

@@

\begin{figure}[ht!]
    \script{spline_basis_plot.py}
        \includegraphics[width=0.45\textwidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing proper MSpline bases with 20 degrees of freedom and equal weights for each component.}
        \label{fig:spline_basis}
\end{figure}

>>>>

\begin{figure}[ht!]
    \script{spline_basis_plot.py}
        \includegraphics[width=0.45\textwidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing a ``proper'' MSpline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
        In black we show the resulting spline function with given equal weights and denote the location of the knots with grey x's.}
        \label{fig:spline_basis}
\end{figure}

@@
